\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage{siunitx}
\usepackage[margin=2cm]{geometry}
\usepackage[nonumber]{cuisine}
\usepackage{microtype}
\usepackage{xpatch}
\usepackage{amsmath}
\usepackage{amssymb}
\makeatletter
\xpatchcmd{\Displ@ySt@p}{\arabic{st@pnumber}}{}{}{}
\makeatother

\begin{document}

\begin{recipe}
  {Baked Prosciutto Crostini with Brie and Apple Butter}
  {}
  {30 minutes}

\freeform{\emph{Crostini? Is that a fancy word for an open-faced
sandwich? --- Husband}}

\Ingredient{1 loaf crusty French bread}
\Ingredient{4 tbsp butter, softened}
\Ingredient{1 cup apple (or pumpkin) butter}
\Ingredient{16 slices prosciutto (about \fr{1}{4} pound)}
\Ingredient{2 apples thinly sliced}
\Ingredient{1 pound brie, thinly sliced}
\Ingredient{Kosher salt}
\Ingredient{ground black pepper}
\Ingredient{olive oil}

Heat the oven to $450^\circ$F.

\medskip

Cut \fr{1}{2}-inch thick, slightly angled slices out of the loaf.
Butter the bottom side of the bread slices and put them onto a parchment lined
baking sheet.
Spread the apple (or pumpkin) butter onto each slice.

\medskip

Top each piece with 1 slice of prosciutto and 1 -- 2 slices of pear or
apple.
Cover this with the Brie slices, season with salt and pepper, and drizzle with
olive oil.
Bake until the cheese is melted, about 8 to 10 minutes.

\end{recipe}


\begin{recipe}
  {Brussels Sprout Gratin with Chestnuts, Bacon and Caramelized
  Shallots}
  {1 pot}
  {60 minutes}

Preheat oven to $375^\circ$F.

\Ingredient{\textbf{The shallots}}
\Ingredient{6 peeled shallots, sliced thin}
\Ingredient{4 tablespoons butter}
\Ingredient{Kosher salt}

In a saut\'{e} pan add the butter.
When butter has melted add shallots and a pinch of kosher salt.
Reduce heat to medium low and continue to cook the shallots, stirring
occasionally, until they are soft and browned (12--15 minutes).
DO NOT LET THEM BURN!
If they brown too quickly, add 1 tablespoon of water, stir, and continue
cooking.
Once they are ready, set them aside.
When the shallots caramelize, make the topping.


\Ingredient{\textbf{The topping}}
\Ingredient{3 cups coarse fresh bread crumbs}
\Ingredient{3 Tablespoons unsalted butter (melted)}
\Ingredient{1 \fr{1}{2} teaspoon lemon zest (about 1 lemon)}
\Ingredient{\fr{1}{2} teaspoon kosher salt}
\Ingredient{\fr{1}{2} ground pepper}
\Ingredient{2 tablespoons minced fresh flat-leaf parsley}

In a bowl, stir together the bread crumbs, melted butter, lemon zest, salt,
pepper, and parsley.
Set aside.


\Ing{\textbf{Brussels sprouts}}
\Ing{2 lb. Brussels sprouts, bottoms trimmed, halved lengthwise}

Bring a large pot of salted water to a boil over high heat.
Add the Brussels sprouts (sliced half lengthwise) and cook until just tender,
5--7 minutes.
Drain, then transfer to a bowl of ice water.
Drain well.


\Ing{\textbf{For the gratin}}
\Ing{\fr{1}{2} lb thick cut smoked bacon sliced into lardons}
\Ing{10 canned chestnuts, diced}
\Ing{2 Tablespoons flour}
\Ing{8 oz Gruy\`ere cheese, grated}
\Ing{2 oz Parmigiano-Reggiano cheese, grated}
\Ing{1 teaspoon lemon zest}
\Ing{\fr{3}{4} teaspoon ground pepper}
\Ing{1 cup heavy cream}
\Ing{olive oil}

In a medium saut\'e pan add 1 tablespoon olive oil and the bacon.
Cook until bacon renders and is just starting to get crisp.
Toss in the drained Brussels sprouts and chopped chestnuts.
Stir well, coating the Brussels sprouts.
Reduce heat to low, sprinkle the flour over the Brussels sprouts, and stir well.
Add the cream and lemon zest, stir and scrape up any bits on the bottom of the
pan.
When the cream begins to bubble and thicken SLIGHTLY, shut off the heat.

\newstep

Pour the Brussels mixture into a large bowl and mix in the Gruy\`ere,
Parmigiano-Reggiano, lemon zest, caramelized shallots, the 2 teaspoons salt, and
the pepper.
Transfer the mixture to the gratin dish and smooth the top.
Sprinkle the bread crumb mixture evenly on top.
Bake until the bread crumbs are golden brown, about 35 minutes.
let the gratin rest for 15 minutes before serving.

\end{recipe}


\begin{recipe}{Green Bean Casserole with Crispy Shallots}
  {1 pot}
  {60 minutes}

Preheat the oven to $375^\circ$F.

\Ing{\fr{1}{4} cup olive oil}
\Ing{6 medium shallots, sliced into rings (about 1 cup)}

Heat the olive oil in a small skillet over medium-high heat until very hot but
not smoking.
Add \fr{1}{4} cup shallots and cook, stirring, until golden brown and
crisp, about 2 minutes.
Transfer with a slotted spoon to paper towels to drain.

\medskip

Repeat with the remaining shallots, cooking \fr{1}{4} cup at a time.
Reserve the oil in the skillet.


\Ing{1.5 pounds thin fresh string beans}

Place the green beans in a steamer basket fitted over boiling water. Cover and
steam until bright green and still crisp, about 3 minutes. (Alternately, just
boil them).
Drain and shock with cold water.
Drain again and reserve in a large bowl.


\Ing{1 pound button mushrooms, sliced}
\Ing{6 large cloves garlic, minced}
\Ing{1 tablespoon chopped fresh thyme}

Heat 1 tablespoon of the reserved shallot oil in a large, deep, nonstick skillet
over medium-hich heat.
Add the mushrooms and cook, stirring occasionally, until the mushroom liquid is
evaporated and they begin to brown, about 12 minutes.
Add the garlic and thyme and cook, stirring, 1 minute.
Transfer the mushroom mixture to the bowl with the green beans.


\Ing{2 cups milk}
\Ing{3 tablespoons flour}
\Ing{\fr{1}{2} finely chopped parsley}
\Ing{\fr{1}{4} ground nutmeg}
\Ing{\fr{1}{2} cup plus 2 tablespoons grated parmesan cheese}
\Ing{1 tablespoon Dijon}
\Ing{salt and pepper}

Whisk together the milk and flour until the flour is mostly dissolved.
Add the mixture to the skillet and, whisking constantly, bring to a simmer.
Reduce the heat to mediumlow, whisking occasionally, until thickened, 10 to 15
minutes. (It will continue to thicken in the oven as well, so don't panic if it
looks slightly soupy).
Remove the pan from heat and stir in the green beans, mushroom mixture, Dijon,
\fr{1}{2} cup parmesan cheese, parsley, nutmeg, \fr{3}{4} teaspoon
salt and \fr{1}{2} teaspoon pepper.

\bigskip

Coat a 2-quart baking dish with cooking spray or olive oil.
Spoon the green bean mixture into the prepared dish and sprinkle the top with
the crispy shallots and the remaining 2 tablespoons parmesan cheese.
Bake until golden on top and bubbling, about 20 minutes.

\end{recipe}

\newpage

\begin{recipe}{Apple Cheesecake with Streusel Topping}
  {1 pie's worth}
  {45 minutes + 3 hours chilling}

\freeform \emph{This may have been designed for mini-cheesecakes, but who has ever
thought they only want a mini-cheesecake? --- Husband}

\Ing{\textbf{For the crust}}
\Ing{10 graham crackers sheets, finely crushed (1 \fr{1}{3} cups)}
\Ing{2 \fr12 tablespoons sugar}
\Ing{\fr14 teaspoon ground cinnamon}
\Ing{6 tablespoons unsalted butter, melted}

Preheat oven to $325^\circ$F.
In a mixing bowl\footnote{Alternately, use husband power.}, whisk together graham cracker
crumbs, sugar and cinnamon.
Pur in butter and using a fork, stir until evenly moistened.
Place mixture along bottom of pie-tin, and press into an even layer.
Bake in a oven for 3--5 minutes, then remove from oven and allow to cool.


\Ing{\textbf{For the streusel}}
\Ing{\fr12 cup flour}
\Ing{\fr14 cup quick oats}
\Ing{\fr12 cup + 2 tablespoons packed light-brown sugar}
\Ing{\fr14 teaspoon ground cinnamon}
\Ing{\fr18 teaspoon ground nutmeg}
\Ing{\fr18 teaspoon salt}
\Ing{\Fr14 cup unsalted butter, cold and diced into \fr12 inch cubes}

In a mixing bowl\footnote{see previous footnote}, whisk together flour, quick
oats, brown sugar, cinnamon, nutmeg, and salt.
Add cold butter and using fingertips, rub butter into dry mixture until it comes
together in small crumbles and pices of butter are no longer visible.\Transfer
to refridgerator while preparing apples and filling.


\Ing{\textbf{For the filling}}
\Ing{2 (8 oz) pkgs cream cheese, softened (16 oz total)}
\Ing{\fr23 cup granulated sugar}
\Ing{2 large eggs from happy chickens}
\Ing{\fr14 cup sour cream}
\Ing{1 teaspoon vanilla extract}
\Ing{1 pound apples peeled, cored, and finely chopped}
\Ing{2 teaspoon lemon juice}

In a bowl, toss chopped apples with lemon juice. Set aside.

In a mixing bowl, using an electric hand mixer\footnote{see previous footnote},
cream together cream cheese with sugar until just smooth. Mix in eggs one at a
time, then blend in sour cream and vanilla.

Resist the urge to devour.

\Ing{\textbf{Assembly}}

Pour filling over crust.
Apply an even layer of apples over crust, and then finish by sprinkling streusel
evenly over the top.

Bake in oven for 12--15 minutes.
Cool at room temperature 30 minutes, then transfer to fridge and chill 3 hours.

\end{recipe}



\end{document}
